### 2013-08-21 proposal/proposal/chapter4.tex
Changes

\setcounter{chapter}{4}

\chapter{Conclusion and Future Work}

\section{Conclusion}\label{sec:conclusion}
In this paper, we proposed a new set of uncertainty measures for the agents in argumentation-based negotiation dialogues from an
external agent's point of view. Specifically, we introduced two types of uncertainty measures: 1) Type I, the uncertainty index of
playing the right move at each dialogue step; and 2) Type II, the uncertainty degree of the agent that the move will be accepted by
the addressee.
For uncertainty Type I, we used Shannon entropy to assess the agents' uncertainty/certainty about their moves in the negotiation
dialogues. We supposed that an external agent is monitoring the dialogue, and he wants to evaluate this dialogue in terms of the
agent's uncertainty/certainty about selecting the right move at each step. In fact, at each step, the agent is supposed to have
different choices, each choice is associated with a probability of being the right one, %which represents the risk of failure for this move to be accepted by the addressee.
this probability reflects the importance of information included in that move, where the higher the probability is, the
more certain the agent becomes (lower uncertainty). So we analyzed the fact that negotiating agents are rational, and they always
try to perform the actions that will result in the optimal outcome for themselves. We used Shannon entropy to measure: i) the
uncertainty/certainty index and the weighted uncertainty/certainty index of the agent that he is playing the right move at each
step during the dialogue; and ii) the uncertainty/certainty index and the weighted uncertainty/certainty index of both agents
participating in the dialogue about the whole dialogue. This was done in two different ways. The first is by taking the average of
the uncertainty index of all moves, and the second is by determining all possible dialogues and applying the general formula of Shannon entropy.

For uncertainty Type II, we formalized the probability association to the arguments and the uncertainty that the move will be
accepted by the addressee. In this context, we introduced a new classification of arguments based on the notion of risk of failure
and showed that this classification is compatible with the probability that the moves supported by those arguments will be
accepted by the address. An important result of this paper is that the selection and probability ordering mechanisms of arguments
are tractable as they can be performed in polynomial time if arguments are represented in propositional definite Horn logic.

In our proposed measures, the move with the higher certainty (lower uncertainty) index is considered as the best move. We analyzed
the fact that negotiating agents are rational, and they always try to perform the actions that will result in the optimal outcome
for themselves. We started our work with measuring the uncertainty/certainty index of each move at each dialogue step, and in order
to distinguish between two moves with the same certainty index, we assigned weight to each move, which reflects the importance of the
move. Then, we proceeded to the whole dialogue and we measured the uncertainty/certainty index for the dialogue in two different ways,
and we proved that the two ways give the same result. Also, assigning weight to the moves allowed us to compare two different dialogues.
We believe that such measures are very significant and helpful in evaluating the dialogue and the agent's strategies, especially when
they are making a decision and selecting the best moves to achieve an agreement (if one exists) in a timely manner.

\section{Future Work}\label{sec:future}
In this paper, we mainly focused on the classical (i.e., precise) probability theory, particularly the classical Shannonian
information theory to measure the uncertainty. As pointed out in \cite{Harmanec1999}, there are other approaches of measuring
uncertainty in the theories of imprecise probabilities, particularly the Dempster-Shafer theory (also known as the theory
of belief functions) \cite{Shafer76} and the possibility theory \cite{Dubois2001}. As future work, we will study key measurements
in these two theories such as \emph{nonspecificity}, \emph{confusion}, \emph{dissonance}, \emph{discord}, and \emph{strife}, and
we will adapt, define and integrate them in our framework. Combining and aggregating those measurements to finally measure the
total uncertainty will be investigated as well. The requirements of those new metrics as reported in \cite{Harmanec1999} will be
analyzed. Those requirements are: 1) generalization, meaning that the new uncertainty measures should generalize the uncertainty
measures already established in the classical probability theory; 2) subadditivity, meaning that when the problem is broken into
two orthogonal subproblems, the uncertainty of the original problem should be less than or equal to the sum of uncertainties of the
subproblems; and 3) additivity, meaning that under the assumption of no interaction and no dependency between the subproblems, the
uncertainty of the original problem is equal to the sum of uncertainties of the subproblems.

Another plan for future work is to extend the proposed metrics for other dialogue game types such as persuasion, deliberation,
inquiry and information seeking. We also plan to analyze argumentation-based dialogues to evaluate agent strategies and
analyze them from the optimization perspective. Analyzing the computational complexity of such optimization problems is another
direction for future work. Finally, we plan to analyze multi-party dialogues to which many agents can participate. Extending the
proposed metrics to this type of dialogues is not straightforward. For example, defining the rules of a multi-party negotiation is
much more complicated than two-party dialogues. In fact, multi-party dialogues cannot be simply reduced to many two-party dialogues.

>>>>

\setcounter{chapter}{3}

\chapter{Efficient Coalition Formation for Autonomous Web Services}

\section{Preliminaries}\label{s:preliminaries}

In this section, we discuss the parameters and preliminary
concepts that we use in the rest of the paper.

\subsection{The Architecture}

Our system consists of three main types of entities working
together:

\emph{1) Web services} are rational entities\footnote{The term
rational is used here in the sense that web services are utility
maximizers} providing services to end users. They aim to maximize
their individual income by receiving enough requests from end
users. In order to increase their revenue, web services seek for
more tasks if they have the capacity and throughput to do so. Web
services can join communities to have better efficiency by
collaborating with others, to have access to higher market share,
and to have opportunity of receiving a bigger task pool from end
users. Throughout this paper, in
our equations, we refer to web services as $ws$ and to the set of
web services hosted by a given community as $C$. To simplify the
notation, sometimes we simply write $ws$ instead of $ws \in C$ to
go through the elements $ws$ of the set $C$.

\emph{2) Master Web Services} or the community coordinators, are representatives of the
communities of web services and responsible for their management.
Communities receive requests from users and aim to host a healthy
set of web services to perform the required tasks. They seek to
maximize user satisfaction by having tasks accomplished according
to the desired QoS. In fact, higher user satisfaction will bring
more user requests and increase the market share and revenue of
the community.

\emph{3) Users} generate requests and try to find the best
available services. User satisfaction is abstracted as function of
quantity and quality of tasks accomplished by a given service.
Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.

\subsection{Web Service Parameters}\label{ws_parameters}

Web services come with different quality of service parameters.
These parameters with a short description are listed in Table
\ref{qosws}.

\begin{table}[!t]
\centering
\caption{List of web service QoS parameters.}
\begin{tabular}{|c|c||c|c|}
\hline
\textbf{Parameter} & \textbf{Definition} \\
\hline\hline
$Availability$ & Probability of being available during \\
&a time frame \\
$Reliability$ & Probability of successfully handling \\
&requests during a timeframe\\
$Successability$ & Rate of successfully handled requests \\
$Throughput$ & Average rate of handling requests \\
$Latency$ & The average latency of services\\
$Capacity$ & Amount of resources available\\
$Cost$ & Mean service fee \\
$Regulatory$ & Compliance with standards, law and rules\\
$Security$ & Quality of confidentiality \\
&and non-repudiation\\
\hline
\end{tabular}
\label{qosws}
\end{table}

We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
which has aggregated and normalized each of these parameters to a
real value between 0 and 1. Since requests are not shared among
web services and are distributed among all of them inside a
community, each one of them comes with a given QoS denoted by
$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
aggregation function of the parameters considered in Table
\ref{qosws}. We use this quality output later in evaluating the
community \emph{worth} or \emph{payoff} function.

\subsection{Web Service Communities}\label{webservice-communities}

Figure \ref{fig_community} represents the architecture of web service communities. The communities are essentially an abstract model of web services. They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\begin{figure*}[!t]
\centerline{\includegraphics[width=6.25in]{Figures/community.eps}}
\caption{Architecture of Web Service communities}
\label{fig_community}
\end{figure*}

### 2013-08-21 proposal/proposal/chapter5.tex
Changes

\setcounter{chapter}{5}
\chapter{Milestones}
In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4. This chapter also includes research methodology and future publication plan.

\section {Research Methodology and Time Line}

    \par The goal of the research project of my Ph.D program is to propose a technically and economically feasible architecture for path stability in MANETs environment.

@@

   % To investigate the architecture of MANETs, we will experiment on backup path, protection, transmission range, interference, and multi Path modeling and analysis on 3D MANETs technologies. We will apply an efficient clustering algorithm for the hierarchical placement of equipment in the above mentioned access network architecture. We will develop mathematical models for different architectures. We will also investigate the protection schemes for these architectures.

The time duration of each task includes the modeling of the proposed solution,  its implementation, validation, performance evaluation  and  publication of its outcome.

\section {Publication Plan}

>>>>

\setcounter{chapter}{4}
\chapter{Conclusion and Future Work}
In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4. This chapter also includes research methodology and future publication plan.

\section {Conclusion}

In this report, we proposed a cooperative game theory-based model
for the aggregation of web services within communities. The goal
of our services is to maximize efficiency by collaborating and
forming stable coalitions. Our method considers stability and
fairness for all web services within a community and offers an
applicable mechanism for membership requests and selection of web
services. The ultimate goal is to increase revenue by improving
user satisfaction, which comes from the ability to perform more
tasks with high quality. Simulation results show that our,
polynomial in complexity, approximation algorithms provide web
services and community owners with applicable and near-optimal
decision making mechanisms.

As future work, we would like to perform more analytical and
theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
characteristic function in web service applications. From web service perspective, the
work can be extended to consider web service compositions where a
group of web services having different set of skills cooperate to
perform composite tasks. Also bargaining theory from cooperating
game theory concepts can be used to help web services resolve the
instability and unfairness issues by side payments.

\section {Future Plan and Timeline}

\par text text

@@
